Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-11-15 doc/ms.tex
include new caption for the Piro figure

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Dessart.pdf}
  \caption{
  }
  \label{fig:dessart}
\end{figure}

\textbf{In Figure~\ref{fig:dessart} we compare photometric
observations of \abc\ to the large-$^{56}$Ni yield DD and PDD
models presented in \citet{2014MNRAS.441..532D}. DD and PDD models
with $M_\mathrm{Ni}/M_\odot \la 0.7$ and 0.5, respectively, fail to
match the early luminosity and blue colors of \abc. The PDD models
provide a better match to the observations than the DD models. The
PDD models evolve more rapidly towards blue colors and provide a
better match to the $g$-band flux in the days after explosion.
Furthermore, unlike the DD models, the PDD models exhibit strong
\ion{C}{2} lines that gradually disappear in the $\sim$week after
explosion \citet{2014MNRAS.441..532D}. In detail, the early wiggles
in the \abc\ light curve are not matched by the PDD models, which
exhibit more smooth variations. Nevertheless, the PDD models
presented in \citet{2014MNRAS.441..532D} provide several attractive
explanations for the unusual features in the early behavior of
\abc, and small adjustments to the model (e.g., additional mixing
of the radioactive material, which \citeauthor{2014MNRAS.441..532D}
only explore for the DD model) may better match \abc. }

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{iPTF16abc_Ni_lc.pdf}
  \caption{Photometric comparison of \abc\ and the theoretical 
  models of \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni 
  mixing in the SN ejecta increases from the short-dash, dark lines 
  to the long-dash, light lines.
  \textit{Top}: $M_g$ vs.\ time, where the observed $g$-band 
  magnitudes  
  have been corrected to $M_g$ using the distance modulus to \abc\ 
  (\S\ref{sec:host})
  and the total line-of-sight reddening ($E(B-V) = 0.08 \; 
  \mathrm{mag}$; Ferretti et al.\ 2017, submitted). The orange 
  solid line shows the model with the most $^{56}$Ni mixing 
  shifted to an explosion time of $t_0 - 0.4 \; \mathrm{d}$. This 
  model provides a good match to the data.
  \textit{Bottom}: $(g' - r')_0$ vs.\ time. The observed colors 
  have been corrected for reddening.
  }
  \label{fig:Ni56LC}
\end{figure}

In Figure~\ref{fig:Ni56LC} we compare model calculations from
\citet{2016ApJ...826...96P} to the observed photometry of \abc. The
\citeauthor{2016ApJ...826...96P} models employ a piston driven explosion to
explode a single WD progenitor model. As the piston explosion does not result
in any nucleosynthesis, the distribution of $^{56}$Ni in the ejecta must be
prescribed by hand, which enables a study of the effects of mixing on the
resulting SN emission. Each model employs a fixed $0.5\,\sm$ of $^{56}$Ni
that has been distributed throughout the ejecta via boxcar averaging (see
their Figure~1). The resulting light curves are synthesized using the
SuperNova Explosion Code (\texttt{SNEC}; \citealt{2015ApJ...814...63M}), as
shown in Figure~\ref{fig:Ni56LC}. Broadly speaking, the results can be
summarized as follows: SN with strong mixing exhibit a rapid almost linear
rise and quickly develop blue colors, whereas models where the $^{56}$Ni is
confined to the innermost layers of the ejecta remain very faint for days
after explosion while exhibiting relatively red optical colors during this
period. The fast rise and blue color of \abc\ are qualitatively consistent
with the strong mixing models from \citet{2016ApJ...826...96P}, as shown in
Figure~\ref{fig:Ni56LC}. In fact, if we adopt $t_\mathrm{exp} = t_0 - 0.4 \,
\mathrm{d}$, we find that the model with the strongest mixing (orange line in
Figure~\ref{fig:Ni56LC}) provides an excellent match to the $g$-band
observations.

While the models from \citet{2016ApJ...826...96P} provide a good match to the
optical photometric evolution of \abc, they consistently overpredict the flux
in the UV. The models shown in Figure~\ref{fig:Ni56LC} also overpredict the
photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$.
Future modeling efforts may improve the match between the simulations and
observations for \abc.

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Dessart.pdf}
  \caption{
  \textbf{Comparison of the DD and PDD models of \citet{2014MNRAS.441..532D}
  to the \abc\ $g$-band light curve (\textit{top}) and the $(B-V)_0$ color curve (\textit{bottom}). The
  light curve has been corrected for the distance modulus to \abc\
  (\S\ref{sec:host}), while both the light curve and color curve have been
  corrected for reddening. Each light curve is translated to match the LCO
  observations $\sim$1.7\,d after $t_0$ given the uncertain time of explosion.
  Translational offsets are listed in the bottom panel legend, which shows the
  models in order of decreasing $M_\mathrm{Ni}$ from top to bottom. DD models
  (labeled as DDC to match the nomenclature of \citealt{2014MNRAS.441..532D})
  are shown as dash-dot lines, while PDD models (labeled as PDDEL) are shown
  as dashed lines. The inset in the top panel shows the residuals relative to
  the PDDEL7n model. The PDD models provide a better match to the
  observations.} 
  } \label{fig:dessart} 
\end{figure}

\textbf{In Figure~\ref{fig:dessart} we compare photometric observations of
\abc\ to the large-$^{56}$Ni yield DD and PDD models presented in
\citet{2014MNRAS.441..532D}. DD and PDD models with $M_\mathrm{Ni}/M_\odot \la
0.7$ and 0.5, respectively, fail to match the early luminosity and blue colors
of \abc. The PDD models provide a better match to the observations than the DD
models. The PDD models evolve more rapidly towards blue colors and provide a
better match to the $g$-band flux in the days after explosion. Furthermore,
unlike the DD models, the PDD models exhibit strong \ion{C}{2} lines that
gradually disappear in the $\sim$week after explosion
\citet{2014MNRAS.441..532D}. In detail, the early wiggles in the \abc\ light
curve are not matched by the PDD models, which exhibit more smooth variations.
Furthermore, while the focus of this study is the early evolution of \abc, the
PDD models evolve more rapidly to the red post-peak than the observations.
Nevertheless, the PDD models presented in \citet{2014MNRAS.441..532D} provide
several attractive explanations for the unusual features in the early behavior
of \abc, and small adjustments to the model (e.g., additional mixing of the
radioactive material, which \citeauthor{2014MNRAS.441..532D} only explore for
the DD model) may better match \abc.}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Piro.pdf}
  \caption{  
  \textbf{Same as Figure~\ref{fig:dessart}, featuring models from
  \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni mixing in the SN ejecta
  increases from the short-dash, light lines to the long-dash, dark lines.
  Unlike Figure~\ref{fig:dessart}, each model features the same
  $M_\mathrm{Ni}$, while the model names reflect the boxcar widths used to
  approximate the effects of mixing in the ejecta (see
  \citealt{2016ApJ...826...96P}). The top panel inset shows the
  residuals relative to the $0.25\,M_\odot$ model. The observations are best
  matched by the $0.25\,M_\odot$ model, i.e. the model with the most
  significant mixing.}
  }
  \label{fig:piro}
\end{figure}

In Figure~\ref{fig:piro} we compare model calculations from
\citet{2016ApJ...826...96P} to the observed photometry of \abc. The
\citeauthor{2016ApJ...826...96P} models employ a piston driven explosion to
explode a single WD progenitor model. As the piston explosion does not result
in any nucleosynthesis, the distribution of $^{56}$Ni in the ejecta must be
prescribed by hand, which enables a study of the effects of mixing on the
resulting SN emission. Each model employs a fixed $0.5\,\sm$ of $^{56}$Ni
that has been distributed throughout the ejecta via boxcar averaging (see
their Figure~1). The resulting light curves are synthesized using the
SuperNova Explosion Code (\texttt{SNEC}; \citealt{2015ApJ...814...63M}), as
shown in Figure~\ref{fig:piro}. Broadly speaking, the results can be
summarized as follows: SN with strong mixing exhibit a rapid almost linear
rise and quickly develop blue colors, whereas models where the $^{56}$Ni is
confined to the innermost layers of the ejecta remain very faint for days
after explosion while exhibiting relatively red optical colors during this
period. The fast rise and blue color of \abc\ are qualitatively consistent
with the strong mixing models from \citet{2016ApJ...826...96P}, as shown in
Figure~\ref{fig:piro}. In fact, if we adopt $t_\mathrm{exp} = t_0 - 0.4 \,
\mathrm{d}$, we find that the model with the strongest mixing (orange line in
Figure~\ref{fig:piro}) provides an excellent match to the $g$-band
observations.

While the models from \citet{2016ApJ...826...96P} provide a good match to the
optical photometric evolution of \abc, they consistently overpredict the flux
in the UV. The models shown in Figure~\ref{fig:piro} also overpredict the
photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$.
Future modeling efforts may improve the match between the simulations and
observations for \abc.
